Validate Structural Analysis \\ \large Testing GPV Method in First-Price Reverse Auctions

### 2020-12-06 paper/paper.tex
delete footnote about github

\section[title]{Simulation 
\footnote{This paper is still a work in progress and I am investigating the 
reason why the result is so. For the latest version on this section, please 
see \url{https://github.com/QuRyu/CDOT/blob/main/paper/paper.pdf }} } 
To test if the estimated cost distribution captures the underlying cost 
distribution that induces observed bids, I will proceed to validation stage: 
simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. For the test data, 
I will use an auction from the dataset which has 16 bidders. The data is not used 
to estimate the cost distribution because the total number of bids with 
$16$ bidders is less than $32$.

>>>>

\section[title]{Simulation} 
To test if the estimated cost distribution captures the underlying cost 
distribution that induces observed bids, I will proceed to validation stage: 
simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. For the test data, 
I will use an auction from the dataset which has 16 bidders. The data is not used 
to estimate the cost distribution because the total number of bids with 
$16$ bidders is less than $32$.
